Are we living in a depressive society?

### 2024-04-04 outputs/paper/paper.qmd
commit
figure

@@

>>>>

# Read the data
age_data <- read.csv(file = here::here("outputs/data/Age_subgroup_trends.csv"))

# Ensure 'Date' column is in Date format
age_data$Date <- as.Date(age_data$Date, format = "%Y-%m-%d")

# Filter data to include only the relevant age subgroups
filtered_data <- age_data %>%
  filter(Subgroup %in% c("18 - 29 years", "30 - 39 years", "40 - 49 years", "50 - 59 years", "60 - 69 years", "70 - 79 years", "80 years and above"))

# Specific date for labeling
label_date <- as.Date("2022-03-02")

# Prepare label data
label_data <- filtered_data %>%
  group_by(Subgroup) %>%
  filter(Date == label_date) %>%
  ungroup()

# Plotting the line graph
graph_A <- ggplot(filtered_data, aes(x = Date, y = Value, color = Subgroup)) +
  geom_line(size = 0.4) +
  geom_hline(yintercept = seq(0, 50, by = 10), color = "lightgrey") +
  geom_text(data = label_data,
            aes(label = Subgroup, y = Value + 2), hjust = 1.1, size = 3) +
  scale_y_continuous(name = "Syptom Rates (%)") +
  scale_x_date(date_breaks = "4 months", date_labels = "%Y-%m-%d") +
  labs(title = "Trend of Depressive Disorder Symptoms by Age Group",
       x = NULL,
       y = "Symptom Rates (%)") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = -45, hjust = 1),
        plot.title = element_text(size = 10),
        legend.position = "none")

# Display the plot
print(graph_A)

@@

```{r}
